---
lang: en
title: "NeoIPC Surveillance Reference Report"
params:
  reportingPeriodFrom: NULL
  reportingPeriodTo: NULL
  birthWeightFrom: NULL
  birthWeightTo: NULL
  gestationWeeksFrom: NULL
  gestationWeeksTo: NULL
  reportingCountries: NULL
  hospitalFilter: NULL
  testUnitFilter: true
  defaultPatientFilter: true
  token: NULL
---

{{< include _setup2.qmd >}}

`{r} translations$headerList$createdAt`:

:   `{r} format(Sys.time(), format = "%x %X", tz = "UTC", usetz = TRUE)`

`{r} translations$headerList$analysisPeriod`:

:   `{r} paste(format(reportingPeriodFrom, format = "%x"), format(reportingPeriodTo, format = "%x"), sep = " - ")`

`{r} if(nrow(data$metadata$countries) > 1){translations$headerList$countries}else{translations$headerList$country}`:

:   `{r} paste0(data$metadata$countries |> arrange(displayName) |> pull(displayName), collapse = ", ")`

`{r} translations$headerList$birthweightFilter`:

:   `{r} if(birthWeightFrom == 0L && birthWeightTo == 2147483647L) translations$headerList$allBirthweights else if(birthWeightFrom == 0) paste0(c("≤ ", format(birthWeightTo), " g"), collapse = "") else if(birthWeightTo == 2147483647L) paste0(c("≥ ", format(birthWeightFrom), " g"), collapse = "") else paste0(c(format(birthWeightFrom), " g - ", format(birthWeightTo), " g"), collapse = "")`

`{r} translations$headerList$gestationalAgeFilter`:

:   `{r} if(gestationWeeksFrom == 0L && gestationWeeksTo == 2147483647L) translations$headerList$allGestationalAges else if(gestationWeeksFrom == 0) paste0(c("≤ ", format(gestationWeeksTo), " w"), collapse = "") else if(gestationWeeksTo == 2147483647L) paste0(c("≥ ", format(gestationWeeksFrom), " w"), collapse = "") else paste0(c(format(gestationWeeksFrom), " w - ", format(gestationWeeksTo), " w"), collapse = "")`

```{r Countries hint}
#| echo: false
#| output: asis

if(nrow(data$metadata$countries) > 1){
  cat(sep = "\n", c(
    "::: {.callout-note}",
    paste0("## ", translations$headerList$multiCountryHintHeader),
    "",
    translations$headerList$multiCountryHint,
    "",
    translations$headerList$multiCountryHintGoal,
    ":::"))
} else {
  cat(sep = "\n", c(
    "::: {.callout-note}",
    paste0("## ", translations$headerList$singleCountryHintHeader),
    "",
    translations$headerList$singleCountryHint,
    "",
    translations$headerList$singleCountryRepresentativenessHint,
    ":::"))
}
```

```{r Custom report hint}
#| echo: false
#| output: asis

if(!testUnitFilter || !defaultPatientFilter){
  cat(sep = "\n", c("::: {.callout-note}", paste0(
    c(
    translations$headerList$specialAnalysisHint,
    if(!testUnitFilter){
      paste0(translations$headerList$includesTestDepartments,
      if(!defaultPatientFilter)
        translations$headerList$and
      else
        ".", collapse = "")
    },
    if (!defaultPatientFilter)
      translations$headerList$ignoresInclusionCriteria
    ), collapse = " "),
    ":::"))
}
```

{{< pagebreak >}}

# Introduction

This document is the reference report of the NeoIPC Surveillance. It contains information about nosocomial infections, the causative infectious agents and associated risk and protective factors that has been collected by partners from multiple neonatology departments who share a passion for preventing infection in neonates. The following numbers present a short overview over the current data set:

Number of partner departments contributing at least one patient record:

:   `{r} format(nrow(data$metadata$departments), big.mark = locale_sep_mark)`

Number of patient records:

:   `{r} format(neoipcr:::get_risk_population(data)$n_patients, big.mark = locale_sep_mark)`

Number of patient admissions:

:   `{r} format(neoipcr:::get_risk_population(data)$n_enrollments, big.mark = locale_sep_mark)`

Sum of patient days:

:   `{r} format(neoipcr:::get_risk_time(data)$patient_days, big.mark = locale_sep_mark)`

Average surveillance period per patient:

:   `{r} format(neoipcr:::get_risk_time(data)$patient_days / neoipcr:::get_risk_population(data)$n_patients, digits = 2, nsmall = 1, scientific = FALSE)` days

# Patient Population

As the process, although supported by various tools, relies on the collection, interpretation and monitoring of information by qualified professionals, NeoIPC surveillance is currently being targeted at the most common nosocomial infections in high-risk neonates, in order to make it sustainable in a continuous manner in as many settings as possible. This means that patients with a birth weight below 1 500 g or a gestational age below 32 weeks at the time of birth are included into the surveillance database if they are admitted to a ward of participating neonatology department within the first 120 days of life. This results in the composition of the patient population that is shown in @fig-bw and @fig-ga.

{{< include figures2/_bw-figure.qmd >}}

{{< include figures2/_ga-figure.qmd >}}

# Risk and Protective Factors

Next to the inherent risk factors gestational age and birth weight there are also a number of expositional factors that influence the risk of an infant to acquire a multi-drug-resistant pathogen or to develop an infection.

{{< include tables2/_tab-usage-density-rates.qmd >}}

## Surgery

The NeoIPC Surveillance patient population is characterised by a low volume of surgical procedures. In this dataset, only `{r} format(n_surgical_departments, big.mark = locale_sep_mark)` of the partner departments (`{r} format(round(n_surgical_departments / nrow(data$metadata$departments) * 100))`%) recorded any surgical procedures at all.

On the other hand, surgically treated neonates often require more than one operation, so that on average `{r} format(n_procedures_per_patient, digits = 2, nsmall = 1, scientific = FALSE)` operations have been performed for each surgical patient.

{{< include tables2/_tab-surgery-rates.qmd >}}

# Nosocomial infections

{{< include tables2/_tab-incidence-density-rates.qmd >}}

{{< include tables2/_tab-device-associated-incidence-density-rates.qmd >}}

# Infectious Agents

{{< include tables2/_tab-infectious-agent-detection-rate-per-inf-type.qmd >}}

{{< include tables2/_tab-infectious-agent-detection-rate-per-agent.qmd >}}

{{< include tables2/_tab-resistance-test-rate.qmd >}}
