---
lang: en
title: "NeoIPC Surveillance Reference Report"
params:
  reportingPeriodFrom: NULL
  reportingPeriodTo: NULL
  birthWeightFrom: NULL
  birthWeightTo: NULL
  gestationWeeksFrom: NULL
  gestationWeeksTo: NULL
  reportingCountries: NULL
  hospitalFilter: NULL
  testUnitFilter: true
  defaultPatientFilter: true
  token: NULL
---

{{< include _setup.qmd >}}

`{r} translations$headerList$createdAt`:

:   `{r} format(Sys.time(), format = "%x %X", tz = "UTC", usetz = TRUE)`

`{r} translations$headerList$analysisPeriod`:

:   `{r} paste(format(reportingPeriodFrom, format = "%x"), format(reportingPeriodTo, format = "%x"), sep = "ŌĆ»-ŌĆ»")`

`{r} if(nrow(data$metadata$countries) > 1){translations$headerList$countries}else{translations$headerList$country}`:

:   `{r} paste0(data$metadata$countries |> arrange(displayName) |> pull(displayName), collapse = ", ")`

`{r} translations$headerList$birthweightFilter`:

:   `{r} if(birthWeightFrom == 0L && birthWeightTo == 2147483647L) translations$headerList$allBirthweights else if(birthWeightFrom == 0) paste0(c("ŌēżŌĆ»", format(birthWeightTo), "ŌĆ»g"), collapse = "") else if(birthWeightTo == 2147483647L) paste0(c("ŌēźŌĆ»", format(birthWeightFrom), "ŌĆ»g"), collapse = "") else paste0(c(format(birthWeightFrom), "ŌĆ»gŌĆ»-ŌĆ»", format(birthWeightTo), "ŌĆ»g"), collapse = "")`

`{r} translations$headerList$gestationalAgeFilter`:

:   `{r} if(gestationWeeksFrom == 0L && gestationWeeksTo == 2147483647L) translations$headerList$allGestationalAges else if(gestationWeeksFrom == 0) paste0(c("ŌēżŌĆ»", format(gestationWeeksTo), "ŌĆ»w"), collapse = "") else if(gestationWeeksTo == 2147483647L) paste0(c("ŌēźŌĆ»", format(gestationWeeksFrom), "ŌĆ»w"), collapse = "") else paste0(c(format(gestationWeeksFrom), "ŌĆ»wŌĆ»-ŌĆ»", format(gestationWeeksTo), "ŌĆ»w"), collapse = "")`

```{r Countries hint}
#| echo: false
#| output: asis

if(nrow(data$metadata$countries) > 1){
  cat(sep = "\n", c(
    "::: {.callout-note}",
    paste0("## ", translations$headerList$multiCountryHintHeader),
    "",
    translations$headerList$multiCountryHint,
    "",
    translations$headerList$multiCountryHintGoal,
    ":::"))
} else {
  cat(sep = "\n", c(
    "::: {.callout-note}",
    paste0("## ", translations$headerList$singleCountryHintHeader),
    "",
    translations$headerList$singleCountryHint,
    "",
    translations$headerList$singleCountryRepresentativenessHint,
    ":::"))
}
```

```{r Custom report hint}
#| echo: false
#| output: asis

if(!testUnitFilter || !defaultPatientFilter){
  cat(sep = "\n", c("::: {.callout-note}", paste0(
    c(
    translations$headerList$specialAnalysisHint,
    if(!testUnitFilter){
      paste0(translations$headerList$includesTestDepartments,
      if(!defaultPatientFilter)
        translations$headerList$and
      else
        ".", collapse = "")
    },
    if (!defaultPatientFilter)
      translations$headerList$ignoresInclusionCriteria
    ), collapse = " "),
    ":::"))
}
```

{{< pagebreak >}}

# Introduction

This document is the reference report of the NeoIPC Surveillance. It contains information about nosocomial infections, the causative infectious agents and associated risk and protective factors that has been collected by partners from multiple neonatology departments who share a passion for preventing infection in neonates. The following numbers present a short overview over the current data set:

Number of partner departments contributing at least one patient record:

:   `{r} format(nrow(data$metadata$departments), big.mark = locale_sep_mark)`

Number of patient records:

:   `{r} format(neoipcr:::get_risk_population(data)$n_patients, big.mark = locale_sep_mark)`

Number of patient admissions:

:   `{r} format(neoipcr:::get_risk_population(data)$n_enrollments, big.mark = locale_sep_mark)`

Sum of patient days:

:   `{r} format(neoipcr:::get_risk_time(data)$patient_days, big.mark = locale_sep_mark)`

Average surveillance period per patient:

:   `{r} format(neoipcr:::get_risk_time(data)$patient_days / neoipcr:::get_risk_population(data)$n_patients, digits = 2, nsmall = 1, scientific = FALSE)` days

# Patient Population

As the process, although supported by various tools, relies on the collection, interpretation and monitoring of information by qualified professionals, NeoIPC surveillance is currently being targeted at the most common nosocomial infections in high-risk neonates, in order to make it sustainable in a continuous manner in as many settings as possible. This means that patients with a birth weight below 1ŌĆ»500ŌĆ»g or a gestational age below 32 weeks at the time of birth are included into the surveillance database if they are admitted to a ward of participating neonatology department within the first 120 days of life. This results in the composition of the patient population that is shown in @fig-bw-ref and @fig-ga-ref.

{{< include figures/_fig-bw-ref.qmd >}}

{{< include figures/_fig-ga-ref.qmd >}}

# Risk and Protective Factors

Next to the inherent risk factors gestational age and birth weight there are also a number of expositional factors that influence the risk of an infant to acquire a multi-drug-resistant pathogen or to develop an infection. @tbl-usage-density-rates shows the presence of these factors in the NeoIPC Surveillance population.

{{< include tables/_tbl-usage-density-rates.qmd >}}

## Surgery

The patient population in neonatology departments is typically characterised by a low volume of surgical procedures. In this dataset, `{r} format(n_surgical_departments, big.mark = locale_sep_mark)` of the partner departments (`{r} format(round(n_surgical_departments / nrow(data$metadata$departments) * 100))`%) recorded surgical procedures during the surveillance period of included neonates.

On the other hand, surgically treated neonates often require more than one operation, so that on average `{r} format(n_procedures_per_patient, digits = 2, nsmall = 1, scientific = FALSE)` operations have been performed for each surgical patient.

While we currently don't calculate surgical site infection rates due to their low volume (n = `{r} format(nrow(data$ssiData), digits = 2, nsmall = 1, scientific = FALSE)` in this dataset), @tbl-surgery-rates gives an overview of the categories of procedures performed in neonates.

{{< include tables/_tbl-surgery-rates.qmd >}}

# Nosocomial infections

Nosocomial infections represent the primary endpoint of NeoIPC surveillance. In @tbl-incidence-density-rates, the incidence densities of sepsis/BSI, pneumonia and necrotising enterocolitis, as well as the combined endpoint 'severe infection', are displayed. Device-associated infections can be found in @tbl-device-associated-incidence-density-rates.

{{< include tables/_tbl-incidence-density-rates.qmd >}}

{{< include tables/_tbl-device-associated-incidence-density-rates.qmd >}}

## Infectious Agents

Epidemiology of the infectious agents causing nosocomial infections in neonatology is complex and there is a lot of potential for bias. While low diagnostic sensitivity (low blood volume) and specificity (contamination) are a general problem in the neonatal population, the lack of availability of some or all means of microbiological diagnostics or the lack of financial resources can have a strong effect on the detection rates in resource-constrained settings.

<!-- When comparing data with the information on pathogens presented in @tbl-infectious-agent-detection-rate-per-agent and information on drug resistance in @tbl-abr-infection-rate, please also have a look at the infectious agent detection rates presented in @tbl-infectious-agent-detection-rate-per-inf-type and the antibiotic resistance test rates in @tbl-resistance-test-rate. -->

When comparing data with the information on pathogens presented in @tbl-infectious-agent-detection-rate-per-agent, please also have a look at the infectious agent detection rates presented in @tbl-infectious-agent-detection-rate-per-inf-type.

{{< include tables/_tbl-infectious-agent-detection-rate-per-agent.qmd >}}

<!-- {{< include tables/_tbl-abr-infection-rate.qmd >}} -->

{{< include tables/_tbl-infectious-agent-detection-rate-per-inf-type.qmd >}}

<!-- {{< include tables/_tbl-resistance-test-rate.qmd >}} -->
